NEED TITLE

### 2014-09-30 ms.tex
included angular momentum

@@

This fully developed turbulent state is the initial condition to which we add self-gravity and sink particle formation for
our star formation experiments. Sink particles are formed as described in Lee et al. (2014). {\bf INCLUDE EQUATION}.  Note that this is different from the sink particle prescription Federrath et al (???) when additional checks need to be performed.

@@

{\bf include discussion of mesh refinement}

{\bf include discussion of star formation.}

@@

@@

{\bf DISCUSS RIGHT PANEL}

@@

A hint of why these different behaviors emerge from looking at the $M(r)$.  In Figure \ref{fig:mass_example}, we plot the mass as a function of radius.  Regions where $M(r)$ flattens implies that the mass in this region can be treated using a point mass approximation.  Here it is apparent that the regions that can be treated a point mass corresponds to regions in where the density follows a $r^{-3/2}$ power law and the radial and turbulent velocities follow a $r^{-1/2}$ power law.

@@

>>>>

\section{Detailed Simulations of Turbulent Collapse}

@@

This fully developed turbulent state is the initial condition to which we add self-gravity and sink particle formation for
our star formation experiments. Sink particles are formed as described in Lee et al. (2014) and described briefly below.

@@

We have also implemented a new algorithm for mesh refinement in these simulations.  As gas collapse under self gravity, certain regions rapidly increase in density.  These regions are refine when the Truelove criterion ($\lambda \le 4 \Delta x$) is met. This corresponds to a condition on the density 
\begin{equation}
refinement criteria
\end{equation}
which when met causes the local grid to be refined by a factor of 2 provide that the maximum refinement level is not reached.

When the Truelove criterion is met at highest refinement level, the excess mass in a cell is transferred either to a newly created sink particle or to a sink particle whose accretion radius includes the cell.  This behavior is the same as in Lee et al. (2014), albeit at a much higher resolution.  We should also note that like Lee et al. (2014), our sink particle creation prescription is different from the prescription of Federrath et al (???) where additional checks need to be performed.

@@

\subsection{Examples of Collapse}

@@

@@

A hint of why these different behaviors emerge from looking at the $M(r)$.  In Figure \ref{fig:mass_example}, we plot the mass as a function of radius.  Regions where $M(r)$ flattens implies that the mass in this region can be treated using a point mass approximation.  Here it is apparent that the regions that can be treated a point mass corresponds to regions in where the density follows a $r^{-3/2}$ power law and the radial and turbulent velocities follow a $r^{-1/2}$ power law.  This is due to mass concentration at smaller radii as evident by the sudden drop in $M(r)$ at $r \approx 10^{-2}$ pc.

@@

\begin{figure*}
\plottwo{Track_0256_000_l.png}{Track_0132_000_l.png}
\caption{WRITE CAPTION: Mass, $MSun$, as a function of radial position from a local maximum density point.     \label{fig:angular_momentum_example}}
\end{figure*}

\subsection{Average Profiles}
